From Reversible Programs to \\ Univalent Universes and Back

### 2021-10-30 Pi/paper/applications.tex
More edits

Solving this problem in the circuit representation is difficult. However, we can observe that all \Afun{toffoli₃} gates
implement even permutations, that is, permutations that perform an even number of transpositions. On the other hand,
\Afun{toffoli₄} implements an odd permutation. It can be easily proved that any composition of even permutations always
produces an even permutation, which answers the question to the negative. Thus, we formulate the theorem using the
representation of lists of transpositions, and transfer it to circuits using the equivalences proven in the previous
sections.

>>>>

Solving this problem in the circuit representation is difficult. However, we can observe that all \Afun{toffoli₃} gates
implement even permutations, that is, permutations that contain an even number of transpositions. On the other hand,
\Afun{toffoli₄} implements an odd permutation. It can be easily proved that any composition of even permutations always
produces an even permutation, which answers the question to the negative. Thus, we formulate the theorem using the
representation of lists of transpositions, and transfer it to circuits using the equivalences proven in the previous
sections.

### 2021-10-30 Pi/paper/reversible1.tex
More edits

\noindent The full set of level-2 combinators is large; the remaining combinators are listed in~\cref{app:leveltwo}.

>>>>

\noindent The full set of level-2 combinators is large; the remaining combinators are listed in~\cref{app:leveltwo} in
the appendix of the extended version~\cite{choudhurySymmetriesReversibleProgramming2021}, and also in the accompanying
Agda formalisation~\cite{choudhuryArtifactSymmetriesReversible2021}.
